Download data

### 2024-02-16 scripts/subsetDataforCrews.Rmd
made roads

blm <- vect(
  '/media/steppe/hdd/Geospatial_data/Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp')

@@

@@

@@

blm_surf <- st_read(paste0(p, 'Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp'), quiet = TRUE)
invasives <- rast(paste0(p, 'MRLC/', '2023_InvGrassCover.tif'))
change_intensity <- rast(paste0(p, 'MRLC/total_change_intensity_index/', 'TCII_3arc.tif'))
fire_perimeters <- st_read(
  paste0(p, 'NIFC_perimeters/', 'InterAgencyFirePerimeterHistory_All_Years_View-Simplified.shp'))

>>>>

blm <- st_read( quiet = T,
  '/media/steppe/hdd/Geospatial_data/Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp') %>% 
  st_transform(5070)

@@

blm <- filter(blm, Unit_Nm %in% seniors$FieldOffice)

@@

Gather together roads data
```{r Gather Roads data}
library(tigris)

states <- states() %>% 
  filter(STUSPS %in% c('NV', 'UT', 'CA', 'AZ', 'CO')) %>% 
  select(STUSPS, ST_NAME = NAME, STATEFP) %>% 
  st_drop_geometry()

county <- counties(states$STUSPS) %>% 
  st_transform(5070)
county <- county[ lengths( st_intersects(county, blm)) > 0, ]

county_rds <- roads(county$STATEFP[1], county$COUNTYFP[1]) %>% 
  st_transform(st_crs(blm))

p2 <- '/media/steppe/hdd/Geospatial_data/blmRoadsSOS24/raw/'

road_setter <- function(x){

  statefp <- x$STATEFP[1]
  county_rds <- lapply(X = x$STATEFP, county = x$COUNTYFP, FUN = tigris::roads) %>% 
    dplyr::bind_rows() %>% 
    sf::st_transform(5070)
  blm_roads <- sf::st_intersection(county_rds, blm)

  st_write(blm_roads, paste0(p2, statefp, '.shp'))
}

rs <- split(county, f = county$STATEFP)
lapply(rs, road_setter)

roads <- lapply(paste0(p2, list.files(p2, pattern = 'shp$')), sf::st_read, quiet = TRUE) |>
  dplyr::bind_rows() %>% 
  select(LINEARID)

roads_simp <- st_simplify(roads, dTolerance = 10)
object.size(roads_simp)/10^9 # ~55% of original size. 
st_write(roads_simp, '/media/steppe/hdd/Geospatial_data/blmRoadsSOS24/processed/BLM_roads.shp', append = F)

rm(states, county, p2, roads, roads_simp, rs, road_setter)
```

@@

blm_surf <- st_read(paste0(p, 'Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp'), quiet = TRUE)
usfs_surf <- st_read(paste0(p, 'Public_land_ownership/USFS_West_simplified/USFS_West_simplified.shp'), quiet = TRUE)
invasives <- rast(paste0(p, 'MRLC/', '2023_InvGrassCover.tif'))
change_intensity <- rast(paste0(p, 'MRLC/total_change_intensity_index/', 'TCII_3arc.tif'))
fire_perimeters <- st_read( quiet = T,
  paste0(p, 'NIFC_perimeters/', 'InterAgencyFirePerimeterHistory_All_Years_View-Simplified.shp'))
SWSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'desertSW/desert_southwest_provisional_seed_transfer_zones_USGS.shp')) %>% 
  select(Zone)
BOWERSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'WWETAC_STZ/GB_2013_revised_reduced.shp')) %>% 
  select(seed_zone)
